\interlude[7]{Epilogue}

\begin{frame}[T]{Epilogue}
  \begin{columns}[fullwidth,t]
      \begin{column}{.45\linewidth}
        \begin{block}{Rosenpass\strut}
          \small
          \begin{itemize}
            \item post-quantum secure AKE
            \item same security as WireGuard
            \item improved state disruption resistance
            \item transfers key to WireGuard for hybrid security
          \end{itemize}
        \end{block}
        \vfill
        \textbf{rosenpass.eu}
      \end{column}

      \begin{column}{.45\linewidth}
        \begin{block}{About Protocols\strut}
        \small
          \begin{itemize}
            \item it is possible to treat NIKEs as KEMs with DHKEM
            \item the GHP Combiner can be used to combine multiple KEMs
            \item X-Wing makes this easy
            \item wall clocks are not to be trusted
          \end{itemize}
        \end{block}
      \end{column}
  \end{columns}
\end{frame}

\begin{frame}[T]{How to engage (karo@rosenpass.eu)}

  \vspace{0.8em}
  We have research projects on…
  \vspace{0.3em}

  \begin{columns}[fullwidth]
    \hfill
    \begin{column}{.3\linewidth}
      \stretchcolumn{
        \begin{block}{Application Security}
        \small
          \begin{itemize}
            \item …\textbf{broker architectures} (multiple low-privilege processes for extra security).
            \item …running Rosenpass in a \textbf{microkernel}.
            \item …implementing \textbf{unix socket based APIs} so other applications can use Rosenpass without security loss.
          \end{itemize}
        \end{block}
      }
    \end{column}

    \hfill

    \begin{column}{.3\linewidth}
      \stretchcolumn{
        \begin{block}{Cryptography\strut}
          \small
          \begin{itemize}
            \item …defend against \textbf{Denial Of Service} attacks using Cryptography.
            \item …using \textbf{Quantum Key Distribution} together with Rosenpass.
            \item …\textbf{error-resistant symmetric ciphers} for radio communication and steganography.
          \end{itemize}
        \end{block}
        \vfill
        }
    \end{column}
    
    \hfill

    \begin{column}{.3\linewidth}
      \stretchcolumn{
        \begin{block}{Social Impact}
          \small
          \begin{itemize}
            \item …how to improve the \textbf{usability} of Rosenpass.
            \item …how to make sure cryptography is useful for \textbf{marginalized groups}.
            \item …how to engage with \textbf{political stakeholders}.
            \item …using \textbf{transdisciplinary approaches} in cryptographic research.
          \end{itemize}
      \end{block}
      \vfill
      }
    \end{column}
    \hfill
  \end{columns}
\end{frame}
